---
title: "Assignment 3 - Data 607"
author: "Coco Donovan"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Identifying Majors with "DATA" or "STATISTICS"

```{r}
library(readr)
library(tidyverse)

majors_url = "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"
majors <- read_csv(majors_url)

str_subset(majors$Major, pattern = "(DATA|STATISTICS)")
```

## 2. Converting Data into a vector

```{r}
library(stringr)

fruits <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"'

fruits_vector <- str_extract(fruits, "\".*\"")
```


## 3. Describe, in words, what these expressions will match:

1. Any character repeated three times (except a newline character).
2. Any two non-newline characters followed by the same two 
non-newline characters in reverse order.
3. Any two non-newline characters repeated in the same order (two characters
followed by the same characters in the same order).
4. Any non-newline character followed by any non-newline character, followed by
the original character, followed by any non-newline character and finally 
followed by the original character.
5. A pattern starting with any three non-newline characters, followed by any 
amount (including zero) of non-newline characters. This pattern is then ended by
the three characters that started the pattern, but in reverse order.


## 4. Construct regular expressions to match words that:

Note: I am operating with the rule that words can only contain letters

```{r}
words <-c('ono', 'jelly', 'pop', 'lol', 'theeth', 'jhoojh', 'qafqa', "eee", 
          "elelel", "olpojo", "jokollo", 'chchlop')

# 4.1: Start and end with the same character
same_first_last <- str_subset(words,"^([a-zA-Z])[a-zA-Z]*\\1$")
same_first_last

# 4.2: Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
repeated_pair <- str_subset(words, "([a-zA-Z][a-zA-Z])[a-zA-Z]*\\1")
repeated_pair

# 4.3: Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
same_letter_3x <- str_subset(words, '([a-zA-Z])[a-zA-Z]*\\1[a-zA-Z]*\\1')
same_letter_3x
```
